\section{Conclusion}
\noindent When developing this project, our teams can learn how to collaborate with each other. We know how to design our UI, and implement our knowledge about databases and architecture into reality. Moreover, we have the opportunity to build a reality program which can solve our problems such as online bus tickets. On the other hand, we can learn a lot of things about databases, performance, scalability, and security. This project helps us have a real experience in terms of developing web applications, which is very popular nowadays. Although our project has a lot of limitations, this application can be considered as a full functionality app which has a login page, shows the bus ticket information, and processes the booking with online payments.

\subsection{Limitations}
\noindent Our application needs a lot of upgrades to become a typical web application. We need to deploy our website, include more payment methods and third-party sign in , build mobile app versions, make the app more responsive, have a function to send tickets to email, design our ticket, add more security methods.

\subsection{Experiences}
\noindent When building our application, we learn how to use PHP languages for back-end, use docker to collaborate, process real live data from front-end to back-end, design minimalist UI, and fix bugs. 

\subsection{Future Development}
\noindent We have to solve our limitations when we have opportunity to develop our project more:
\begin{itemize}
    \item Fixing our UI
    \item Hosting our website
    \item Including third-party sign in
    \item Building mobile app
    \item Building mobile version
    \item Designing our tickets
\end{itemize}
