\section{Introduction}

\subsection{Objective}
\noindent The VGU Bus Ticket Booking System final report, which includes a technical description of the program's architecture and the data flow through the program, is submitted in order to fulfill the criteria of the Programming Exercise course. Our main objective is to create a web-based platform for the booking system so that the Vietnamese-German University can utilize it to control the transportation component. The staff and students' user experiences will improve as a result.

\subsection{Audience}
\noindent The course instructor, Professor Huynh Trung Hieu, who will also be in charge of giving grades, will be the target audience for this paper. We also present our project to students in Computer Science class (intake 2020).

\subsection{Project Scope}
\noindent The purpose of this report is to inform the reader about the characteristics of the software and to update them on the project's status and timetable. This report does not include a thorough explanation of the framework utilized, the applications, or the functions. We must meet the following requirements in order to declare this project a success:
\begin{itemize}
    \item An effective method for purchasing bus tickets that makes it simple for students to order and examine their tickets, each of which includes a QR code.
    \item Using a QR scanner, drivers can scan the tickets.
    \item Administrators have the ability to change the ticket pricing and add new notifications that are visible to both students and drivers.
    \item Momo API should be used to complete the payment.
    \item Google API should be used to generate the QR Code and verify the Captcha code.
    \item A Dockerfile should be included with the source code to run the project.
    \item Students can easily view their bus ticket information by using our web application.
\end{itemize}

\subsection{Constraints}
\noindent When completing the project, we encountered these challenges:
\begin{itemize}
    \item Lack of professional project working experience.
    \item Ineffective when using PHP with JavaScript.
    \item Some functions in front-end part do not work as expected.
    \item Lack of other payment methods (such as Paypal, credit card).
    \item Cannot sign in by other common platforms (Google accounts, Github accounts, Facebook accounts). 
    \item Our application response is quite slow.
\end{itemize}

\noindent The project has a deadline of completing within 8 weeks, but considering our unfamiliarity with all the necessary tools and programming languages, we believe that extending the deadline could enhance the project. A little more time to learn about the tools and refine our skills can go a long way in improving the final product. 